---
title: "region report"
output: html_document
params:
   region: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Dropbox/gsa_2017/")
```

---
title: GSA Region `r params$region` Energy Data Exchange
---

This document captures the past five years of portfolio energy performance for your region in comparison to your peers. Beginning with a National Overview, the document dives into the building EUAS data for xx GSA owned facilities in your region. Energy use
totals, energy use per square foot, LEAN analysis, and buildings with the greatest cost savings compared to national medians are identified. Prior energy saving investment outcomes from a national overview are profiled alongside selected case studies of
successful energy retrofits in your region.

## 2017 Building Count and Square Footage

```{r count_by_type}

getwd()
devtools::load_all("~/Dropbox/gsa_2017/summarise.and.plot")
summarise.and.plot::national_overview(category=c("A", "C", "I"), year=2017)
```
