---
title: "ROI calculation"
author: "Yujie Xu"
date: "8/21/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

## Introduction

In this document we demonstrated how the simplified ROI is calculated for two example buildings

The following information are needed for the retrofit ROI calculation: retrofit action, retrofit time, retrofit budget, energy and weather data before the retrofit, energy and weather data after the retrofit.

Following we'll demonstrate for a single building how the ROI analysis is conducted.

<!-- replace this -->
The building is "UT0032ZZ"
```{r ecm, echo=FALSE}
# building = "UT0032ZZ"
# building = "OK0063ZZ"
# building = "IL0302ZZ"
# building = "IN1703ZZ"
# building = "GA0138ZZ"
# 10 ROI ---------------
# building = "DC0028ZZ"
# building = "LA0098ZZ"
# building = "NY0300ZZ"
# building = "NY0351ZZ"
# building = "NY0399ZZ"
# building = "SC0028ZZ"
# building = "NC0028ZZ"
# building = "FL0061ZZ"
# building = "OK0063ZZ"
building = "UT0032ZZ"
library("devtools")
library("dplyr")
#getwd()
devtools::load_all("~/Dropbox/gsa_2017/db.interface")
devtools::load_all("~/Dropbox/gsa_2017/get.noaa.weather")
devtools::load_all("~/Dropbox/gsa_2017/lean.analysis")
devtools::load_all("~/Dropbox/gsa_2017/roiForECM")
action =
  dfECM %>%
  dplyr::filter(`Building_Number`==building) %>%
  dplyr::mutate(`action_time`=lubridate::ymd(`Substantial_Completion_Date`)) %>%
  dplyr::select(`Building_Number`, `high_level_ECM`, `detail_level_ECM`, `action_time`) %>%
  {.}
print(action)
```

We'll retrieve the before and after period for both actions

```{r period, echo=FALSE}
library(lubridate)
load("~/Dropbox/gsa_2017/roiForECM/data/analysisStartEnd.rda")
timeframe = analysisStartEnd %>%
  dplyr::filter(`Building_Number`==building) %>%
  {.}
print(head(timeframe))
action_times = timeframe$`action_time`
```

Then retrieve energy data

```{r energy, echo=FALSE}
buildingEnergy = energy %>%
  dplyr::select(-`Electric_(kBtu)`, -`Gas_(kBtu)`) %>%
  dplyr::filter(`Building_Number`==building) %>%
  dplyr::mutate(`Date`=lubridate::ymd(sprintf("%.0f-%.0f-01", `year`, `month`))) %>%
  {.}
buildingEnergy %>%
  head()
```

Plot electricity data and action time

```{r plotTrendEnergy, echo=FALSE, out.width='60%', fig.align='center'}
par(mfrow = c(2,1))
p = buildingEnergy %>%
  ggplot2::ggplot(ggplot2::aes(y=`Electricity_(KWH)`, x=`Date`)) +
  ggplot2::ylab("Electricity(KWH)") +
  ggplot2::xlab("Time") +
  ggplot2::geom_line()
for (t in action_times) {
  p <- p + ggplot2::geom_vline(xintercept=t, linetype="dashed",
                               color="red")
}
p <- p + ggplot2::theme_bw()
print(p)
ggplot2::ggsave(sprintf("%s_elec_trend.png", building), width=8, height=4)
p = buildingEnergy %>%
  ggplot2::ggplot(ggplot2::aes(y=`Gas_(Cubic_Ft)`, x=`Date`)) +
  ggplot2::ylab("Gas(Cubic Foot)") +
  ggplot2::xlab("Time") +
  ggplot2::geom_line()
for (t in action_times) {
  p <- p + ggplot2::geom_vline(xintercept=t, linetype="dashed",
                               color="red")
}
p <- p + ggplot2::theme_bw()
print(p)
ggplot2::ggsave(sprintf("%s_gas_trend.png", building), width=8, height=4)
```

Get utility cost

```{r utility_cost}
buildingUtilityCost =
  utilityCost %>%
  dplyr::filter(`Building_Number`==building) %>%
  dplyr::mutate(`Date`=lubridate::ymd(sprintf("%.0f-%.0f-01", `year`, `month`))) %>%
  dplyr::arrange(desc(`Date`)) %>%
  {.}
print(head(buildingUtilityCost))
```

Plot utility cost

```{r utilityCost, echo=FALSE, out.width='60%', fig.align='center'}
par(mfrow = c(2,1))
p = buildingUtilityCost %>%
  ggplot2::ggplot(ggplot2::aes(y=`Electric ($/KWH)`, x=`Date`)) +
  ggplot2::xlab("Time") +
  ggplot2::geom_line()
for (t in action_times) {
  p <- p + ggplot2::geom_vline(xintercept=t, linetype="dashed",
                               color="red")
}
p <- p + ggplot2::theme_bw()
print(p)
ggplot2::ggsave(sprintf("%s_elec_cost.png", building), width=8, height=4)
p = buildingUtilityCost %>%
  ggplot2::ggplot(ggplot2::aes(y=`Gas ($/Cubic Ft)`, x=`Date`)) +
  ggplot2::xlab("Time") +
  ggplot2::geom_line()
for (t in action_times) {
  p <- p + ggplot2::geom_vline(xintercept=t, linetype="dashed",
                               color="red")
}
p <- p + ggplot2::theme_bw()
print(p)
ggplot2::ggsave(sprintf("%s_gas_cost.png", building), width=8, height=4)
```

Use the most recent three year's average utility cost in the ROI analysis

```{r avgUtility}
utilityRateElec = mean(head(buildingUtilityCost, n=36)$`Electric ($/KWH)`)
utilityRateGas = mean(head(buildingUtilityCost, n=36)$`Gas ($/Cubic Ft)`)
sprintf("Electricity utility rate: %.2f $/KWH", utilityRateElec)
sprintf("Gas utility rate: %.2f $/Cubic Foot", utilityRateGas)
```

Get weather data (use getWeatherData.R) from NOAA GHCND, variable definitions can be found [here]{ftp://ftp.ncdc.noaa.gov/pub/data/ghcn/daily/readme.txt}

```{r weather}
library(feather)
weather =
  feather::read_feather(sprintf("../../data-raw/building_TAVG/compiled/%s_TAVG.feather", building)) %>%
  tibble::as_data_frame() %>%
  dplyr::mutate(`year`=year(`Date`),
                `month`=month(`Date`)) %>%
  dplyr::group_by(`year`, `month`) %>%
  dplyr::summarise(`Monthly Mean Temperature`=mean(`TAVG`)) %>%
  dplyr::ungroup() %>%
  {.}
print(head(weather))
```

Join weather and energy data

```{r energyWeather}
energy_weather = buildingEnergy %>%
  inner_join(weather, by=c("year", "month")) %>%
  {.}
print(head(energy_weather))
```

## Lean Analysis

```{r leanPlots, fig.align='center', fig.asp=0.6}
setwd("~/Dropbox/gsa_2017")
roiForECM::add_lean(building=building)
```

## Fit models

```{r fitModel}
setwd("~/Dropbox/gsa_2017")
roiBuilding(building=building)
```