---
title: "skysparkEDA_0117"
author: "Yujie Xu"
date: "1/17/2019"
output:
  powerpoint_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

## Tasks completed

- Downloaded the set of completed sparks
- Downloaded ION domestic water data
- Augmented the previous analysis with building area

---

## Presence of energy and water data

```{r buildingSet, results='asis'}
library("dplyr")
library("readxl")
library("ggplot2")
library("purrr")
gsalink_building =
  readxl::read_excel("../data-raw/list_of_gsalink_buildings.xlsx",
                     sheet=2) %>%
  tibble::as.tibble() %>%
  dplyr::mutate(`building`=substr(`spark_entry`, 1, 8)) %>%
  dplyr::select(-`spark_entry`) %>%
  dplyr::filter(`status`=="downloaded") %>%
  dplyr::select(-`status`) %>%
  {.}
energy_status = 
  readr::read_csv("../data-raw/energy_data_existance.csv")
summaryTable = gsalink_building %>%
  dplyr::left_join(energy_status) %>%
  dplyr::mutate_if(is.numeric, function(x) ifelse(is.na(x), 0, x)) %>%
  {.}
summaryTable %>%
  readr::write_csv("../data-raw/gsalink_energy_data_existance.csv")
rowPerPage = 11
numPages = floor(nrow(summaryTable) / rowPerPage)
for (i in 1:(numPages)) {
  tmp <- summaryTable %>%
    slice((i * rowPerPage):((i + 1) * rowPerPage)) %>%
    knitr::kable(digits = 1) %>%
    {.}
  print(tmp)
}
```

---

# 2018 Rule data by building

---

<!-- result='asis' makes kable print look normal -->
```{r rule, results='asis'}
library("dplyr")
library("ggplot2")
dfrule = readr::read_csv("../data-raw/rule_summary.csv") %>%
  tibble::as.tibble() %>%
  {.}
dfname = readr::read_csv("../data-raw/downloaded_building_name.csv") %>%
  dplyr::select(`Building_Number`, `name_last`) %>%
  dplyr::rename(`building`=`Building_Number`, `name`=`name_last`) %>%
  {.}
dfrule <- dfrule %>%
  dplyr::left_join(dfname, by="building") %>%
  {.}
df_area = readr::read_csv("../data-raw/gsalink_building_area.csv")
sumByBuilding = dfrule %>%
  dplyr::group_by(`building`) %>%
  summarise(`# rules`=n(), count=sum(count),
            `total cost`=sum(Cost),
            `total duration`=sum(`duration_hour`)) %>%
  dplyr::ungroup() %>%
  dplyr::left_join(df_area) %>%
  {.}
rowPerPage = 11
numPages = floor(nrow(sumByBuilding) / rowPerPage)
for (i in 1:(numPages)) {
  tmp <- sumByBuilding %>%
    dplyr::arrange(desc(`total cost`)) %>%
    slice((i * rowPerPage):((i + 1) * rowPerPage)) %>%
    knitr::kable(format.args=list(big.mark = ','), digits = 1) %>%
    {.}
  print(tmp)
}
```

# top ranking rules based on three criteria

## 2018 Rule data top 10 by number of buildings affected

```{r ruleMostBuilding}
sumByRule = dfrule %>%
  dplyr::left_join(df_area) %>%
  dplyr::group_by(`rule`) %>%
  summarise(`# buildings`=n(), count=sum(count), `total cost`=sum(Cost),
            `total duration`=sum(`duration_hour`), `total GSF`=sum(GSF)) %>%
  dplyr::ungroup() %>%
  {.}
top10 = sumByRule %>%
  dplyr::select(`rule`, `# buildings`, `total GSF`) %>%
  dplyr::arrange(desc(`# buildings`)) %>%
  head(n=10) %>%
  {.}
top10 %>%
  knitr::kable(format.args=list(big.mark = ','))
```

## 2018 Rule data top 10 by total duration (hour)

```{r ruleMostDuration}
top10 = sumByRule %>%
  dplyr::select(`rule`, `total duration`, `total GSF`) %>%
  dplyr::arrange(desc(`total duration`)) %>%
  dplyr::mutate(`duration/GSF`=`total duration` / `total GSF`) %>%
  dplyr::select(-`total GSF`) %>%
  head(n=10) %>%
  {.}
top10 %>%
  knitr::kable(format.args=list(big.mark = ','))
```

## Most affected buildings

```{r top5, results='asis'}
rules = top10$rule[1:5]
for (r in rules) {
  tmp <- dfrule %>%
    dplyr::filter(rule == r) %>%
    dplyr::arrange(desc(`duration_hour`)) %>%
    dplyr::select(`building`, `name`, `rule`, `duration_hour`) %>%
    head(n=5) %>%
    dplyr::left_join(df_area) %>%
    dplyr::mutate(`duration/GSF`=`duration_hour`/`GSF`) %>%
    knitr::kable(format.args=list(big.mark = ','), digits = 1) %>%
    {.}
  print(tmp)
}
```

## 2018 Rule data top 10 by highest cost

```{r ruleMostCost}
top10 <- sumByRule %>%
  dplyr::select(`rule`, `total cost`, `total GSF`) %>%
  dplyr::arrange(desc(`total cost`)) %>%
  head(n=10) %>%
  dplyr::mutate(`cost/GSF`=`total cost` / `total GSF`) %>%
  dplyr::select(-`total GSF`) %>%
  {.}
top10 %>%
  knitr::kable(format.args=list(big.mark = ','))
```

## Most affected buildings

```{r top5cost, results='asis'}
rules <- top10$rule[1:5]
for (r in rules) {
  tmp <- dfrule %>%
    dplyr::filter(rule == r) %>%
    dplyr::arrange(desc(`Cost`)) %>%
    dplyr::select(`building`, `name`, `rule`, `Cost`) %>%
    head(n=5) %>%
    dplyr::left_join(df_area) %>%
    dplyr::mutate(`cost/GSF`=`Cost`/`GSF`) %>%
    knitr::kable(format.args=list(big.mark = ','), digits = 1) %>%
    {.}
  print(tmp)
}
```

# Rankings excluding sensor or data related rules: "Missing Data", "Sensor Out Of Range", "Sensor Failure", and "Bad Energy Data"

## 2018 Rule data top 10 by number of buildings affected

```{r ruleMostBuildingFilter}
rulesToExclude = c("Missing Data", "Sensor Out Of Range", "Sensor Failure", "Bad Energy Data")
top10_nbuilding = sumByRule %>%
  dplyr::select(`rule`, `# buildings`, `total GSF`) %>%
  dplyr::filter(!(`rule` %in% rulesToExclude)) %>%
  dplyr::arrange(desc(`# buildings`)) %>%
  head(n=10) %>%
  {.}
top10_nbuilding %>%
  knitr::kable(format.args=list(big.mark = ','))
```

## 2018 Rule data top 10 by total duration (excluding data error)

```{r ruleMostDurationFilter}
top10_dur = sumByRule %>%
  dplyr::select(`rule`, `total duration`, `total GSF`) %>%
  dplyr::filter(!(`rule` %in% rulesToExclude)) %>%
  dplyr::arrange(desc(`total duration`)) %>%
  head(n=10) %>%
  dplyr::mutate(`duration/GSF`=`total duration` / `total GSF`) %>%
  dplyr::select(-`total GSF`) %>%
  {.}
top10_dur %>%
  knitr::kable(format.args=list(big.mark = ','))
```

## 2018 Rule data top 10 by highest cost (excluding data error)

```{r ruleMostCostFilter}
top10_cost = sumByRule %>%
  dplyr::select(`rule`, `total cost`, `total GSF`) %>%
  dplyr::filter(!(`rule` %in% rulesToExclude)) %>%
  dplyr::arrange(desc(`total cost`)) %>%
  head(n=10) %>%
  dplyr::mutate(`cost/GSF`=`total cost` / `total GSF`) %>%
  dplyr::select(-`total GSF`) %>%
  {.}
top10_cost %>%
  knitr::kable(format.args=list(big.mark = ','))
```

<!-- # 20 Rules show up in at least one of the criteria, and 3 Rules show up in all three criteria -->

<!-- ## 20 Rules show up in at least one of the criteria -->

<!-- ```{r distinctRules, size='tiny'} -->
<!-- list(top10_nbuilding$rule, top10_dur$rule, top10_cost$rule) %>% -->
<!--   reduce(union) %>% -->
<!--   sort() %>% -->
<!--   print() -->
<!-- ``` -->

<!-- ## 3 Rules show up in all three criteria -->

<!-- ```{r commonRules} -->
<!-- list(top10_nbuilding$rule, top10_dur$rule, top10_cost$rule) %>% -->
<!--   reduce(intersect) %>% -->
<!--   sort() %>% -->
<!--   print() -->
<!-- ``` -->